Extended Data

### 2021-11-17 doc/manuscript/Dow_manuscript_Nature.Rmd
added SPEI refs + a bit of text
@camerondow35 , please verify added sentence.

#89

To rule out the possibility that observed patterns were strongly influenced by summer drought, we examined the relationship between spring tempreatures and summer Standardized Precipitation Evapotranspiration Index[@vicente-serrano_multiscalar_2010].
The latter was obtained from the ForestGEO Climate Data Portal v1.0 (https://forestgeo.github.io/Climate/)[@anderson-teixeira_forestgeo_2020; @begueria_standardized_2017]. Linear models were run with 4-, 6-, and 12-month SPEI values of June, July, and August vs April $T_{max}$ to determine if warm spring temperatures lead to greater summer drought stress.

>>>>

To rule out the possibility that observed patterns were strongly influenced by summer drought, we examined the relationship between spring tempreatures and summer Standardized Precipitation Evapotranspiration Index[@vicente-serrano_multiscalar_2010].
The latter was obtained from the ForestGEO Climate Data Portal v1.0 (https://forestgeo.github.io/Climate/)[@anderson-teixeira_forestgeo_2020; @begueria_standardized_2014;@vicente-serrano_multiscalar_2010a]. 
Linear models were run with 4-, 6-, and 12-month SPEI values of June, July, and August vs April $T_{max}$ to determine if warm spring temperatures lead to greater summer drought stress. 
No significant correlations were found (all p>0.05).
